% LaTeX Template für Abgaben an der Universität Stuttgart
% Autor: Sandro Speth
% Bei Fragen: Sandro.Speth@studi.informatik.uni-stuttgart.de
%-----------------------------------------------------------
% Hauptmodul des Templates: Hier können andere Dateien eingebunden werden
% oder Inhalte direkt rein geschrieben werden.
% Kompiliere dieses Modul um eine PDF zu erzeugen.

% Dokumentenart. Ersetze 12pt, falls die Schriftgröße anzupassen ist.
\documentclass[12pt]{scrartcl}
\input{../Usepackage.tex}
\input{../FormatAndHeader.tex}

\title{Specification}
\date{Wintersemester 18/19}
\author{Sandro Speth\\
Markus Zilch\\
Dominik Wagner}

% Beginn des eigentlichen Dokuments
\begin{document}
\maketitle
\input{./Introduction.tex}

\section{System Design}\label{sec:systemdesign}

\subsection{Difference between $kW$ and $kWh$}\label{sec:diffEnergy}
W is a messuring scale for energy applied per timeinstance.
There are different possibilities to describe $W$ in common terms.
A pretty graphic one is the movement of mass.
$1W$ equals $1kg$ of mass moved by 1 meter in one second: $1 \frac{kg*m^2}{s^3}$.
Or in electrical terms: $1W$ equals 1 Ampere of electrical power with a voltage of 1 Volt.
Both of those formulas are equal to a much simpler Term for Watt: $1 W = 1 J/s$.
In simple terms, 1 Watt is the same as one Joule of energy applied over 1 second.
For completeness, $1kW = 1000 W$.\\
\\
Wh are the common term for messuring energyconsumption/-production.
$1Wh$ is $1W$ applied continuously over 1 hour.
 $1Wh = 1 W * 1h = 1 J/s * 3600s = 3600J$.
 For a scientific context the $Wh$ therefore is simply not used, instead the common SI standard $J$ is used.\\
\\
In comparison, $Wh$ is the total amount of energy used. $W$ is how much energy is used in a specified timeslot (mostly 1 second).\\
\\
Sources:\\
Robert A. Nelson: The International System of Units. Applied Technology Institute\\
\url{https://www.aticourses.com/international_system_units.htm}\\
Gérard Borvon: History of the electrical units. S-eau-S, 10. September 2012\\
\url{http://seaus.free.fr/spip.php?article964}\\
Das Internationale Einheitensystem (SI). Deutsche Übersetzung der BIPM-Broschüre „Le Système international d’unités/The International System of Units (8e édition, 2006)“. In: PTB-Mitteilungen. Band 117, Nr. 2, 2007\\
\url{https://www.ptb.de/cms/fileadmin/internet/Themenrundgaenge/ImWeltweitenNetzDerMetrologie/si.pdf}\\
aufgrund der EU-Richtlinie 80/181/EWG in den Staaten der EU bzw. dem Bundesgesetz über das Messwesen in der Schweiz\\
\url{https://www.admin.ch/opc/de/classified-compilation/20101915/}

\subsection{Difference between consumption and demand}\label{sec:diffconsumptiondemand}
\input{./A2.tex}


\subsection{Userstories}\label{sec:userstories}
\input{./UserStories.tex}

\subsection{Architecture}
System architecture Diagram

\subsection*{A5}
add weather component

\subsection*{A6}
reliable and responsive system

\subsection*{A7}
three-tier system architecture

% Ende des Dokuments
\end{document}
