\begin{enumerate}
\item As a user, I need to create one or more wind turbines in the simulation so that I can calculate the potential energy output.

\item As a user, I need to create one or more photovoltaic panels in the simulation so that I can calculate the potential energy output.

\item As a user, I need to create one or more batteries in the simulation so to save unused energy of in my simulation.

\item As a user, I need to get the charging state of my batteries to know the impact of the energy storage on the grid.

\item As a user, I need to create one or more homes on the demand side in the simulation so that I can simulate some energy consumer.

\item As a user, I need to create one or more commercial buildings on the demand side in the simulation to simulate some high energy consumer.

\item As a user, I need to get dynamic energy prices calculated from the simulation to determine if I want to sell my produced energy or store it for later use.

\item As a user, I need to use weather data in the simulation to simulate the smart energy system more precise and realistic.

\item As a user, I need to use already saved weather data in the simulation to not be dependent on the availability of the weather service.

\item As a user, I need to generate a forecast for energy generation and demand using the simulation in order to make informed decisions.

\item As a developer, I want to add more supplier modules like wind turbines and photovoltaic panels to the simulation to improve the smart energy system in the future with further technology due to adding more kinds of suppliers. 

\item As a developer, I want to add more consumer modules to the simulation to be able to add more kinds of consumers to the simulation. 

\item As a user, I want to be able to create a smart energy system which is independent to a main power grid to simulate a reliable smart grid.

\item As a user, I want to get a visual notification if the supply of energy is smaller than the demand of energy to know when more energy supplier are needed.

%\item As a demand module, I need to get energy from the (charged) batteries if the provided supply is too small for my demand so that I still have enough money. 

\item As a user, I want to model a rechargeable battery so I can store the energy for later usage, if the supply is greater than the demand.

\item As a user, I need the battery to be able to discharge energy if the supply is lower than the demand in order to make my stored energy usable and keep the demand satisfied.

\item As a user, I need the smart grid to be able to manage peaks in the demand in order to smooth the impact on the grid and reduce the likelihood of power outages.

\item As a user, I need that the demand side consumers feature different load scenarios like home users and commercial users (constant load, occasionally peak loads) in order to make the simulation accurate for real life applications.

\item As a user, I want be able to use the system with my webbrowser so that I can use different platforms to view it and have easy access to the simulated data.

\item As a user, I want to be able to see the energy supply of each individual supply component in order to be able to assess the efficiency of the supplier.

\item As a user, I want to be able to see the energy demand of individual components for efficiency assessment and informed decision making. 

\item As a user, I want to see a summary of energy supply and demand for all components in order to easily assess the current situation.

\item As a user, I want to adjust the demand by postponing the use of devices during peak hours in order to prevent a complete outage of the grid or to react to one-time-only scenarios.

\item As a user, I want the simulation to adapt the demand based on the price per kWh in order to minimize costs of my energy demands and maximize profits of my energy supply.

\end{enumerate}

