% LaTeX Template für Abgaben an der Universität Stuttgart
% Autor: Sandro Speth
% Bei Fragen: Sandro.Speth@studi.informatik.uni-stuttgart.de
%-----------------------------------------------------------
% Hauptmodul des Templates: Hier können andere Dateien eingebunden werden
% oder Inhalte direkt rein geschrieben werden.
% Kompiliere dieses Modul um eine PDF zu erzeugen.
% Dokumentenart. Ersetze 12pt, falls die Schriftgröße anzupassen ist.
\documentclass[12pt]{scrartcl}
\input{../Usepackage.tex}
\input{../FormatAndHeader.tex}
\bibliography{bibliography.bib}
\title{Practical course
\\ Smart Energy Systems\\
	Report}
\date{Wintersemester 18/19}
\author{Sandro Speth\\
Markus Zilch\\
Dominik Wagner}

% Beginn des eigentlichen Dokuments
\begin{document}
\maketitle
\input{./Introduction.tex}

\section{System Design}\label{sec:systemdesign}

\subsection{Difference between $kW$ and $kWh$}\label{sec:diffEnergy}
W is a measuring scale for energy applied per time instance.
There are different possibilities to describe $W$ in common terms.
A pretty graphic one is the movement of mass.
$1W$ equals $1kg$ of mass moved by 1 meter in one second: $1 \frac{kg*m^2}{s^3}$.
Or in electrical terms: $1W$ equals 1 Ampere of electrical power with a voltage of 1 Volt.
Both of those formulas are equal to a much simpler Term for Watt: $1 W = 1 J/s$.
In simple terms, 1 Watt is the same as one Joule of energy applied over 1 second.
For completeness, $1kW = 1000 W$ \cite{Nelson,Borvon,SIStandard}.

$Wh$ are the common term for measuring energy consumption and production.
$1Wh$ is $1W$ applied continuously over 1 hour.
$1Wh = 1 W * 1h = 1 J/s * 3600s = 3600J$.
For a scientific context the $Wh$ therefore is simply not used, instead the common SI standard $J$ is used.
In comparison, $Wh$ is the total amount of energy used. $W$ is how much energy is used in a specified timeslot (mostly 1 second) \cite{EURichtlinie,Bundesgesetz}.


\subsection{Difference between consumption and demand}\label{sec:diffconsumptiondemand}
\input{./A2.tex}


\subsection{Userstories}\label{sec:userstories}
\input{./UserStories.tex}

\subsection{Architecture}
\input{./Architecture.tex}

\section{Implementation}\label{sec:Implementation}
\input{./Implementation.tex}

\section{Demand Response and coordination}\label{sec:DemandResponse}
\input{./A3.tex}

\section{Conclusions}
\input{./Conclusion.tex}

\printbibliography
%\bibliographystyle{plain}
%\bibliography{bibliography}
All links were checked last on December 13, 2018.
% Ende des Dokuments
\end{document}
